Expos\'{e} Master Thesis\\ Checking Assertions for Smart Contracts

### 2020-08-18 meeting-notes/20200812-expose.tex
integrated remarks by Ha

@@

There may be an alternative way of implementing this scheme without modifying the
protocol, but instead adding instructions to the virtual machine. One instruction would
generate a random number (EVM uses 512 bit unsigned integer IIRC), the other would
raise an overriding failure. Ideally, once a counterexample has been found, this
counterexample is broadcast to the network where it can be verified by further nodes.

This approach poses the danger of a DOS attack. Someone could post a false
counterexample, which does not really lead to a failure. If everyone switches to check
this proposed counterexample instead of generating a random number, then the real
problem may remain hidden. So, there has to be a component in the protocol that
penalizes someone who broadcasts a false counterexample. Moreover, not all validators
should switch to recheck a proposed counterexample; or they could check it in addition
to their own random check.

>>>>

\usepackage{xcolor}
\usepackage{tcolorbox}
\tcbuselibrary{breakable}

\newenvironment{changethis}{%
  \begin{tcolorbox}[breakable,notitle,boxrule=0pt,colback=blue!20,colframe=blue!20]}{%
  \end{tcolorbox}}

@@

There may be an alternative way of implementing this scheme without modifying the
protocol, but instead adding instructions to the virtual machine. One instruction would
generate a random number (EVM uses 512 bit unsigned integer IIRC), the other would
raise an overriding failure. Ideally, once a counterexample has been found, this
counterexample is broadcast to the network where it can be verified by further nodes.
But this broadcast and the reaction to this broadcast requires an update of the
protocol: all receivers of the broadcast will check the counterexample and revert the
transaction. This probably means that a transaction using this feature has to wait for
a couple of cycles in the transaction pool until the node feels safe to include the
transaction in a block.

\begin{changethis}
  Tezos specific remarks, here the number of validators is really small compared to
  Bitcoin or Ethereum
  \begin{itemize}
  \item maybe we need to propose and validate the same block multiple times before it
    gets accepted. E.g, a transaction containing this feature is only accepted if it is
    revalidated $n$ times.
  \item Extra validators only for this kind of transaction.
  \end{itemize}
\end{changethis}
This approach poses the danger of a DOS attack. Someone could post a false
counterexample, which does not really lead to a failure. If everyone switches to check
this proposed counterexample instead of generating a random number, then the real
problem may remain hidden. So, there has to be a component in the protocol that
penalizes someone who broadcasts a false counterexample. Moreover, not all validators
should switch to recheck a proposed counterexample; or they could check it in addition
to their own random check.
